---
title: "South Delta Gates - channel exploration"
output: 
  flexdashboard::flex_dashboard:
    theme: readable
    orientation: rows
  font_family: "Roboto"
  google_fonts: true
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(leaflet)
library(sf)
library(DT)
library(RColorBrewer)
```

```{r}
channels <- readRDS('data/channels_with_numbers.RDS') |> 
  sf::st_transform(crs = 4326) |> 
  na.omit()

channels_monthly <- readRDS('data/channels_monthly_data.RDS') |> 
  sf::st_transform(crs = 4326)

bbox <- st_bbox(channels)
```

## Inputs {.sidebar data-width="500"}

The scenario `FPV2Mb` is compared to the baseline, with difference values calculated as *scenario value - baseline value* and reported in feet.

Each difference (min, max, mean) represents a comparison of the summarized values for a specific year, month with an option to summarize by month or day. Daily summaries are the summary of daily 5-minute increments. Monthly summarize represent the min, max, or mean of the daily summaries. 

```{r}
radioButtons(inputId = "which_agg", 
             label = HTML("<strong>How to Summarize Data</strong>"),
             choices = c("Daily", "Monthly"))

selectInput(
  inputId = "which_year",
  label = HTML("<strong>Select Year</strong>"),
  choices = 2020:2023,
  selected = 2020
)


sliderInput(
  inputId = "which_month",
  label = HTML("<strong>Select Month</strong>"),
  min = 5,
  max = 11,
  value = 5,
  step = 1,
  ticks = TRUE,
  animate = TRUE
)


conditionalPanel(
  condition = "input.which_agg == 'Daily'",
  sliderInput(
    inputId = "which_day", 
    label = tags$strong("Select Day"),
    min = 1, 
    max = 31, 
    value = 1,
    step = 1, 
    ticks = TRUE, 
    animate = TRUE
  )
)


selectInput(
  inputId = "which_stat", 
  label = HTML("<strong>Select Statistic</strong>"),
  choices = c("Min", "Max", "Mean"), 
  selected = "Mean"
)

output$data_table <- renderDT({
  req(filtered_data()) 
  
  filtered_data() |> 
    st_set_geometry(NULL) |>  
    filter(channel_id %in% c(71, 128, 205)) |> 
    mutate(name = case_when(channel_id == 71 ~ "OLD", 
                            channel_id == 128 ~ "DGL", 
                            channel_id == 205 ~ "MHO")) |> 
    select(name, min_diff, avg_diff, max_diff) |> 
    mutate(
      min_diff = round(min_diff, 1), 
      avg_diff = round(avg_diff, 1),
      max_diff = round(max_diff, 1)
    ) 
}, options = list(
  searching = FALSE,  
  lengthChange = FALSE,  
  paging = FALSE, 
  info = FALSE,
  scrollY = "150" 
))

# Output the data table
DTOutput("data_table")

```

## Column {data-width="100" data-height="100"}

```{r}
filtered_data <- reactive({
  req(input$which_month, input$which_year)
  
  if(input$which_agg == "Monthly") {
    agg <- channels_monthly |>
      filter(month == input$which_month, 
             year == input$which_year) 
  } else {
    agg <- channels |> 
      filter(day == input$which_day,
             month == input$which_month,
             year == input$which_year)
  }
  
  agg |> glimpse()
  
  return(agg)
})

stat <- reactive({
  req(input$which_stat)
  
  switch(input$which_stat, 
         "Min" = 'min_diff', 
         "Max" = 'max_diff',
         "Mean" = 'avg_diff')
  
})

legend_title <- reactive({
  req(input$which_stat)
  
  switch(input$which_stat, 
         "Min" = 'Min Stage Diff (ft)', 
         "Max" = 'Max Stage Diff (ft)',
         "Mean" = 'Mean Stage Diff (ft)')
  
})

# Render Leaflet map
output$map <- renderLeaflet({
  leaflet() |> 
    addTiles(urlTemplate = "https://{s}.basemaps.cartocdn.com/light_all/{z}/{x}/{y}{r}.png",
             attribution = '&copy; <a href="https://www.openstreetmap.org/copyright">OpenStreetMap</a> contributors &copy; <a href="https://carto.com/">CARTO</a>', group = "Street") |> 
    addProviderTiles(
      "Esri.WorldImagery",
      group = "Satellite"
    ) |>
    # Add USGS Topo layer
    addProviderTiles(
      "USGS.USTopo",
      group = "Topographic"
    ) |>
    setView(lat = 37.82116120308882, lng = -121.42962730014777, zoom = 13  
    ) |> 
    addLayersControl(
      baseGroups = c("Satellite", "Street", "Topographic"),
      position = "topright",
      options = layersControlOptions(collapsed = FALSE)
    )
})

# Observe changes and update layers
observe({
  req(filtered_data())
  
  
  channels_merge <- filtered_data()
  current_stat <- stat()
  current_legend_title <- legend_title()
  
  # Define color palette
  data_min <- min(channels_merge$avg_diff, na.rm = TRUE)
  data_max <- max(channels_merge$avg_diff, na.rm = TRUE)
  # Determine the maximum absolute value
  #max_abs_value <- max(abs(c(data_min, data_max)))
  max_abs_value <- range(channels_merge$avg_diff, channels_merge$min_diff, channels_merge$max_diff)
  
  palette <- colorNumeric(
    palette = colorRampPalette(brewer.pal(11, "RdBu"))(100),
    domain = c(-max_abs_value, max_abs_value))
  
  # Update polylines
  leafletProxy("map") |> 
    clearShapes() |> 
    clearControls() |> 
    addPolylines(
      data = channels_merge,
      weight = 7,
      opacity = 1,
      label = ~as.character(channel_id),
      color = ~palette(get(current_stat)),
      popup = ~sprintf(
        "<div style='font-family: Arial; font-size: 12px;'>
        <table style='width: 100%%; border-collapse: collapse; margin: 10px 0;'>
          <tr style='background-color: #f8f9fa;'>
            <td style='padding: 8px; border: 1px solid #dee2e6;'><strong>ID</strong></td>
            <td style='padding: 8px; border: 1px solid #dee2e6;'>%s</td>
          </tr>
          <tr style='background-color: #f8f9fa;'>
            <td style='padding: 8px; border: 1px solid #dee2e6;'><strong>%s</strong></td>
            <td style='padding: 8px; border: 1px solid #dee2e6;'>%.2f ft</td>
          </tr>
        </table>
      </div>",
      as.character(channel_id), current_legend_title, get(current_stat)
      ),
      labelOptions = labelOptions(
        style = list(
          "font-weight" = "bold",
          padding = "3px 8px"
        ),
        textsize = "15px",
        direction = "auto"
      )
    ) |> 
    addLegend(
      position = "bottomright",
      pal = palette,
      values = channels_merge[[current_stat]],
      title = current_legend_title,
      opacity = 1
    )
})

leafletOutput("map", width = "100%", height = "100%")

```

