---
title: "South Delta Gates - channel exploration"
output: 
  flexdashboard::flex_dashboard:
    theme: readable
    orientation: rows
  font_family: "Roboto"
  google_fonts: true
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(leaflet)
library(sf)
library(DT)
library(RColorBrewer)
```

```{r}
# Read in scenarios 
combined_data_b1sa <- readRDS("data/combined_data_b1sa.RDS")
combined_data_b1sb <- readRDS("data/combined_data_b1sb.RDS")

all_data <- list(
  b1sa = combined_data_b1sa,
  b1sb = combined_data_b1sb
)

# read in channel geometry
channels <- readRDS("data/channels_shp.RDS") |> 
  sf::st_transform(crs = 4326)

bbox <- st_bbox(channels)

gates <- channels |> 
  filter(id %in% c(71, 128, 205)) |> 
  mutate(name = case_when(id == 71 ~ "OLD", 
                          id == 128 ~ "MHO", 
                          id == 205 ~ "DGL")) |> 
  select(id, geometry, name) |> 
  distinct() 

```


## Inputs {.sidebar data-width="500"}

<!-- The scenario `FPV2Mb` is compared to the baseline, with  -->

Difference values calculated as *scenario 1 - scenario 2*.

Each difference (min, max, mean) represents a comparison of the summarized values for a specific year, month with an option to summarize by month or day. Daily summaries are the summary of daily 5-minute increments. Monthly summarize represent the min, max, or mean of the daily summaries. 

```{r}
tabsetPanel(
  tabPanel("Map Controls", 
           
           tagList(
             tags$div(
               style = "display: inline-block; vertical-align: top; width: 45%;",
               selectInput("scen1", tags$strong("Scenario 1:"), 
                           choices = c("B1sa" = "b1sa", 
                                       "B1sb" = 'b1sb'),
                           selected = "b1sa")
             ),
             tags$div(
               style = "display: inline-block; vertical-align: top; width: 45%; margin-left: 5%;",
               selectInput("scen2", tags$strong("Scenario 2:"), 
                           choices = c("B1sa" = "b1sa", 
                                       "B1sb" = 'b1sb'),
                           selected = "b1sb")
             ),
             
             selectInput(inputId = "which_variable",
                         label = tags$strong("What Variable"),
                         choices = c("Stage", "EC")),
             
             radioButtons(inputId = "which_agg", 
                          label = HTML("<strong>How to Summarize Data</strong>"),
                          choices = c("Daily", "Monthly")),
             
             selectInput(
               inputId = "which_year",
               label = HTML("<strong>Select Year</strong>"),
               choices = 2020:2023,
               selected = 2020
             ),
             
             
             sliderInput(
               inputId = "which_month",
               label = HTML("<strong>Select Month</strong>"),
               min = 5,
               max = 11,
               value = 5,
               step = 1,
               ticks = TRUE,
               animate = TRUE
             ),
             
             
             conditionalPanel(
               condition = "input.which_agg == 'Daily'",
               sliderInput(
                 inputId = "which_day", 
                 label = tags$strong("Select Day"),
                 min = 1, 
                 max = 31, 
                 value = 1,
                 step = 1, 
                 ticks = TRUE, 
                 animate = TRUE
               )
             ),
             
             
             selectInput(
               inputId = "which_stat", 
               label = HTML("<strong>Select Statistic</strong>"),
               choices = c("Min", "Max", "Mean"), 
               selected = "Mean"
             ), 
             
             #   output$data_table <- renderDT({
             #     req(filtered_data()) 
             #     
             #     filtered_data() |> 
             #       st_set_geometry(NULL) |>  
             #       filter(channel_id %in% c(71, 128, 205)) |> 
             #       mutate(name = case_when(channel_id == 71 ~ "OLD", 
             #                               channel_id == 128 ~ "MHO", 
             #                               channel_id == 205 ~ "DGL")) |> 
             #       select(name, min_diff, avg_diff, max_diff) |> 
             #       mutate(
             #         min_diff = round(min_diff, 1), 
             #         avg_diff = round(avg_diff, 1),
             #         max_diff = round(max_diff, 1)
             #       ) 
             #   }, options = list(
             #     searching = FALSE,  
             #     lengthChange = FALSE,  
             #     paging = FALSE, 
             #     info = FALSE,
             #     scrollY = "150" 
             #   )),
             #   
             # )
             
           )
           #----------------
  ), 
  tabPanel("Settings", 
           tagList(
             selectInput("color_palette", 
                         label="Select Color Palette", 
                         choices = c("Red to Blue"="RdBu", "Purple to Orange"="PuOr", "Purple to Green"="PRGn", "Red Yellow Green"="RdYlGn")), 
             
             sliderInput(inputId = "base_opacity", label = "Select base layer opacity", 
                         min = .5, max = 1, step = .1, value = 1)
           ))
)



```

## Column {data-width="100" data-height="100"}

```{r}
scenario_1 <- reactive({input$scen1})
scenario_2 <- reactive({input$scen2})
which_variable <- reactive({input$which_variable})

scenario_1_data <- reactive({
  req(scenario_1())
  all_data[[scenario_1()]] |> 
    as.data.frame() 
})

scenario_2_data <- reactive({
  req(scenario_2())
  all_data[[scenario_2()]] |> 
    as.data.frame() 
})

scenario_comparison <- reactive({
  req(c(input$scen1, input$scen2))
  
  comparison <- bind_rows(scenario_1_data(), scenario_2_data()) |> 
    janitor::clean_names() |> 
    pivot_wider(
      names_from = scenario,
      values_from = c(daily_avg, daily_min, daily_max)
    ) |> 
    na.omit() 
  
  scenario_cols <- names(comparison)[grepl("^daily_avg_", names(comparison))]
  scenarios <- sub("^daily_avg_", "", scenario_cols)
  
  comparison <- comparison  |> 
    mutate(
      avg_diff = .data[[paste0("daily_avg_", scenarios[1])]] - .data[[paste0("daily_avg_", scenarios[2])]],
      min_diff = .data[[paste0("daily_min_", scenarios[1])]] - .data[[paste0("daily_min_", scenarios[2])]],
      max_diff = .data[[paste0("daily_max_", scenarios[1])]] - .data[[paste0("daily_max_", scenarios[2])]]
    ) 
  
  print("this is the return: ")
  comp_return <- comparison |>
    select(-contains("daily")) |> 
    mutate(month = lubridate::month(date),
           day = lubridate::day(date),
           year = lubridate::year(date)) |> 
    left_join(channels) |>
    glimpse()
  
  return(comp_return)
})

observe({
  req(input$scen1, input$scen2)
  
  comp <- scenario_comparison()
  
})


```

```{r}
filtered_data <- reactive({
  req(input$which_month, input$which_year)
  # 
  if(input$which_agg == "Monthly") {
    agg <- scenario_comparison() |>
      group_by(month, id, year) |>  
      filter(month == input$which_month, 
             year == input$which_year) 
  } else {
    agg <- scenario_comparison() |> 
      group_by(day, month, year, id) |> 
      filter(day == input$which_day,
             month == input$which_month,
             year == input$which_year)
  }
  
  agg 
  
  return(agg)
})

stat <- reactive({
  req(input$which_stat)
  
  switch(input$which_stat, 
         "Min" = 'min_diff', 
         "Max" = 'max_diff',
         "Mean" = 'avg_diff')
  
})

legend_title <- reactive({
  req(input$which_stat)
  
  switch(input$which_stat, 
         "Min" = 'Min Stage Diff (ft)', 
         "Max" = 'Max Stage Diff (ft)',
         "Mean" = 'Mean Stage Diff (ft)')
  
})

output$map <- renderLeaflet({
  leaflet() |> 
    addTiles(urlTemplate = "https://{s}.basemaps.cartocdn.com/light_all/{z}/{x}/{y}{r}.png",
             attribution = '&copy; <a href="https://www.openstreetmap.org/copyright">OpenStreetMap</a> contributors &copy; <a href="https://carto.com/">CARTO</a>', group = "Street", 
             options = tileOptions(opacity = input$base_opacity)) |> 
    addProviderTiles(
      "Esri.WorldImagery",
      group = "Satellite", 
      options = providerTileOptions(opacity = input$base_opacity)
    ) |>
    addProviderTiles(
      "USGS.USTopo",
      group = "Topographic",
      options = providerTileOptions(opacity = input$base_opacity)
    ) |>
    setView(lat = 37.82116120308882, lng = -121.42962730014777, zoom = 13  
    ) |> 
    addLayersControl(
      baseGroups = c("Satellite", "Street", "Topographic"),
      position = "topright",
      options = layersControlOptions(collapsed = FALSE)
    )
})

# observe({
#   req(filtered_data())
#   
#   channels_merge <- filtered_data()
#   current_stat <- stat()
#   current_legend_title <- legend_title()
#   
#   # Define color palette
#   data_min <- min(channels_merge$avg_diff, na.rm = TRUE)
#   data_max <- max(channels_merge$avg_diff, na.rm = TRUE)
#   # Determine the maximum absolute value
#   #max_abs_value <- max(abs(c(data_min, data_max)))
#   max_abs_value <- range(channels_merge$avg_diff, channels_merge$min_diff, channels_merge$max_diff)
#   
#   palette <- colorNumeric(
#     palette = colorRampPalette(brewer.pal(11, input$color_palette))(100),
#     domain = c(-max_abs_value, max_abs_value))
#   
#   leafletProxy("map") |>
#     clearShapes() |> 
#     clearControls() |> 
#     addPolylines(data = gates, 
#                  label = ~name,
#                  labelOptions = labelOptions(permanent = TRUE,  
#                                              direction = "auto",  
#                                              opacity = 1,  
#                                              textOnly = FALSE,  
#                                              style = list(
#                                                "font-weight" = "bold",  
#                                                "font-size" = "14px",  
#                                                "color" = "black",
#                                                "background" = "white",
#                                                "border" = "1px solid black",
#                                                "padding" = "3px"
#                                              ))) |> 
#     addPolylines(
#       data = channels_merge,
#       weight = 7,
#       opacity = 1,
#       label = ~as.character(channel_id),
#       color = ~palette(get(current_stat)),
#       popup = ~sprintf(
#         "<div style='font-family: Arial; font-size: 12px;'>
#         <table style='width: 100%%; border-collapse: collapse; margin: 10px 0;'>
#           <tr style='background-color: #f8f9fa;'>
#             <td style='padding: 8px; border: 1px solid #dee2e6;'><strong>ID</strong></td>
#             <td style='padding: 8px; border: 1px solid #dee2e6;'>%s</td>
#           </tr>
#           <tr style='background-color: #f8f9fa;'>
#             <td style='padding: 8px; border: 1px solid #dee2e6;'><strong>%s</strong></td>
#             <td style='padding: 8px; border: 1px solid #dee2e6;'>%.2f ft</td>
#           </tr>
#         </table>
#       </div>",
#       as.character(channel_id), current_legend_title, get(current_stat)
#       ),
#       labelOptions = labelOptions(
#         style = list(
#           "font-weight" = "bold",
#           padding = "3px 8px"
#         ),
#         textsize = "15px",
#         direction = "auto"
#       )
#     ) |> 
#     addLegend(
#       position = "bottomright",
#       pal = palette,
#       values = channels_merge[[current_stat]],
#       title = current_legend_title,
#       opacity = 1
#     )
# })
# 
# leafletOutput("map", width = "100%", height = "100%")

```

