---
title: "SDG Map Dev"
author: "Maddee Rubenson (FlowWest)"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(leaflet)
library(sf)


knitr::opts_chunk$set(echo = TRUE)
```

## Read in files 

### nodes 

The nodes spatial layer provided by DWR

```{r}
nodes <- sf::read_sf('data-raw/MSS_nodes/dsm2_nodes_newcs_extranodes.shp') |> glimpse()
```

### channels

The channels spatial layer provided by DWR

```{r}
channels <- sf::read_sf('data-raw/fc2024.01_chan/FC2024.01_channels_centerlines.shp') |> glimpse()
```

### output_channel

Data `output_channel` from the .h5 file 

```{r}
channels_with_numbers <- read_csv('data-raw/channel_names_from_h5.csv') |> glimpse()
```

### channel

Data `channel` from the .h5 file 

```{r}
channel <- read_csv('data-raw/channel.csv') |> glimpse()
```

### dss output - scenario

```{r}
dss_hydro_output <- read_csv('data-raw/fpv1ma_hydro_export.csv') |> glimpse()
```
### dss output - baseline 

```{r}
dss_output_baseline <- read_csv('data-raw/h1z_hdro_export.csv') |> glimpse()
```

## Create summaries 

### Scenario 

Create a summary of dss stage output 

```{r}
dss_hydro_summary <- dss_hydro_output |>
  filter(param == "stage") |>
  mutate(node = toupper(node)) |> 
  group_by(node) |>
  summarise(min_stage = min(value),
            max_stage = max(value),
            mean_stage = mean(value)) |>
  mutate(scenario = "FPV1MA") |> 
  glimpse()
```

### Baseline

```{r}
dss_hydro_summary_baseline <- dss_output_baseline |>
  filter(param == "stage") |>
  mutate(node = toupper(node)) |> 
  group_by(node) |>
  summarise(min_stage = min(value),
            max_stage = max(value),
            mean_stage = mean(value)) |>
  mutate(scenario = "baseline") |> 
  glimpse()
```

```{r}
hydro_summary <- dss_hydro_summary_baseline |> 
  full_join(dss_hydro_summary) |>
  group_by(node) |> 
  # NOTE: scenario - baseline diff
  summarise(min_diff = diff(min_stage),
            mean_diff = diff(mean_stage),
            max_diff = diff(max_stage),
            .groups = "drop") |> 
  glimpse()

```



## Join files 

Merge with channels spatial layer 

```{r}
channels_merge <- channels |>
  left_join(channels_with_numbers |>
              rename(id = chan_no) |>
              filter(variable == "stage") |>
              filter(file == "./output/FPV2Mb_hydro.dss")) |>
  sf::st_transform(crs = 4326) |>
  left_join(hydro_summary |> rename(name = node)) |>
  # left_join(dss_hydro_output |> rename(name = node)) |>
  filter(!is.na(name)) |>
  glimpse()

```

## Visuals

```{r}
palette <- colorNumeric(
  palette = "viridis",
  domain = channels_merge$min_diff
)

leaflet() |>
  addTiles(urlTemplate = "https://{s}.basemaps.cartocdn.com/light_all/{z}/{x}/{y}{r}.png",
           attribution = '&copy; <a href="https://www.openstreetmap.org/copyright">OpenStreetMap</a> contributors &copy; <a href="https://carto.com/">CARTO</a>') |>
  addPolylines(
    data = channels_merge,
    color = ~palette(min_diff),
    popup = ~paste0(
      "id = ", id, "<br>",
      "name = ", name, "<br>",
      "min stage difference = ", round(min_diff, 1)
    )
  ) |>
  addLegend(
    position = "bottomright",
    pal = palette,
    values = channels_merge$min_diff,
    title = "Min Stage Diff",
    opacity = 1
  )

```
